`SimSurvey`: an `R` package to optimize the design and analysis of fisheries surveys by simulating spatially-correlated fish stocks

### 2019-07-31 analysis/paper/sim_survey_paper.Rmd
Address Keith's latest suggestions

**1\.** Age-structured fish stocks often show complex spatial and temporal dynamics, creating challenges in designing and implementing effective population surveys. Inappropriate sampling designs can potentially lead to both under-sampling (reducing precision and increasing the risk of bias) and over-sampling (through the extensive sampling of correlated metrics).

**2\.** For assessments based on fisheries-independent surveys, the ability to estimate population parameters is affected by multiple levels of sampling, such as the number of fishing sets and sub-sampling the fish captured to measure biological characteristics (e.g. lengths or ages). Multiple analysis approaches are also now available.

**3\.** Though simulations are a useful tool for exploring the efficacy of specific sampling strategies and statistical methods, complex fish population structure has limited the number of tools that allow for simulation testing of a range of sampling and analytical pathways for fisheries-independent survey data.

**4\.** Here we introduce the `R` package **`SimSurvey`**, which has been designed to simplify the process of simulating surveys of age-structured and spatially-distributed fish populations. The package allows the user to simulate age-structured populations that vary in space and time and then explore the efficacy of a range of sampling protocols to reproduce the population parameters of the known population. **`SimSurvey`** also include a function for running a stratified-random analysis of the simulated data.

**5\.** **`SimSurvey`** can serve as a convenient, accessible and flexible platform for simulating a wide range of sampling strategies for fish stocks that show complex structuring. Various design- or model-based approaches can then be applied to the results to test the efficacy of different analytical approaches.

@@

Fisheries-independent surveys have become a mainstay in the management of dynamic fish stocks as they provide indices of population abundance as well as estimates of various population characteristics such as length and age frequencies [@Pennington1998]. While costly to obtain, this information forms the basis of many stock assessments throughout the world. Efficient and informed management decisions therefore require surveys and analyses that maximize information while minimizing the expense of data collection. While simulations provide a platform for exploring solutions to this optimization problem, building the necessary simulation framework is not a trivial task given the multi-stage nature of the typical sampling program and the complexity of the population processes we aim to represent. Notably, many fish stocks show size-specific patterns of aggregation, making it difficult to collect biological sub-samples (e.g. lengths and ages) that are representative of the entire target population. This undermines the assumptions of many analyses as sub-samples from such populations tend to exhibit strong positive intracluster correlation [@Aanes2015]. These complexities may explain why simulations that test the full sampling and analytical pathway of fisheries-independent surveys are rare [but see @puerta2019; @schnute2003].

Here we document **`SimSurvey`**, an `R` package designed to simplify and facilitate realistic simulations of fisheries-independent trawl surveys. In short, the package allows for the simulation of random or stratified-random surveys of an age-structured population that varies in space and time

The package has two main components, the first focuses on mimicking realistic fish stocks by simulating a spatially and age-correlated population distributed across a habitat gradient, and the second component focuses on simulating various surveys of these virtual fish stocks.

This simulation framework has similarities to those presented by Schnute and Haigh [-@schnute2003] and Puerta et al. [-@puerta2019], however, efforts were focused on developing a series of general and accessible functions to simplify the process of testing multiple sampling scenarios and analytical pathways. The steps taken to simulate surveys of spatial, age-structure populations are outlined below.

@@

Table: (\#tab:fun) Names and descritpions of the key functions of **`SimSurvey`**. Functions in bold font are core functions and those in medium font are designed for use inside the core functions. The latter are typicaly closures, which are functions that contain data and return functions [@wickham2014]; here they are used to store parameter values and return functions that require dimensions, such as ages or years, to be supplied.

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean depth. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation within ages and years, and the two dimension AR1 age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations are controlled by a smoothing ($\lambda$) and a scaling parameter ($\kappa$) [here $\kappa$ is approximated from the range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years is controlled by $\varphi_{\xi, \mathrm{age}}$ and $\varphi_{\xi, \mathrm{year}}$, respectively. The overall variance of the process is controlled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid. A more detailed description of the space-age-year covariance is included in [*Appendix B*][Appendix B: Age-year-space covariance].

@@

This function retains all the data simulated by `sim_abundance` and adds a data.table [@dowle2017], named `sp_N`, with abundance (`N`) split by `age`, `year` and `cell`. The function also retains the grid object and converts these data into a data.table, named `grid_xy`, with headers `x`, `y`, `depth`, `cell`, `division` and `strat`. The `sp_N` object can be merge with the `grid_xy` data by `cell` to associate abundance with specific locations, depth, divisions or strata. The `plot_distribution` function can be used to provide a quick visual of the distribution across ages and years. The code below will generate interactive plots with an Age-Year slider, however, for this paper we present a facet plot of the simulated data (Figure \@ref(fig:distribution)).

@@

The final step in the simulation is to conduct a stratified random survey over the age-year-space array generated. The area of each strata is calculated and this is used to define the number of sets to allocate to each strata under a particular set density, $D_{\mathrm{sets}}$. The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

@@

The function `sim_survey` can be used to simulate data from one survey over a population created using `sim_distribution`. A default function call is described in Table \@ref(tab:survey)). The `sim_survey` function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Multiple simulations of the same survey can be run using the `n_sims` argument, however, requesting large numbers of simulations can be computational demanding depending on the processing capacity available. Below we use `sim_survey` to simulate two surveys over a default population, of which one is set-up to have higher set density (`set_den`) than the other.

@@

```{r survey, fig.cap = "Bubble plots and histograms of set catches from a simulated stratified-random survey of a default population under relatively a) low and b) high sampling effort. Histograms of length and age composition include the distribution of all fish caught next to those sampled overlaid with a line of the true distribution of lengths and ages available to the survey. Note that the first simulation of the survey in year 20 is depicted here. These plots are produced by `plot_survey` when supplied survey data simulated using `sim_survey`."}

@@

As noted above, available RAM may limit the utility of the `sim_survey` function for running thousands of simulations of the same survey. The `sim_survey_parallel` function was therefore constructed to facilitate this process. This function is set-up to run multiple `sim_survey` calls in parallel using the **`doParallel`** package [@weston2015] and, as such, multiple loops can be run using the `n_loops` argument and within each loop multiple simulations can be run (controlled using the `n_sims` argument). Total simulations will be the product of `n_loops` and `n_sims` arguments. If more than one core (`cores`) is specified, then the simulations will be run in parallel to speed up the process. Low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower. The optimum ratio of `n_sims` to `n_loops` will depend on the amount of RAM and number of cores the user's computer has. In any case, this function simplifies the process of running thousands of simulations of the same survey and the simulated data can then be supplied to survey-based or model-based analyses that require simulation testing.

@@

Once the survey data are simulated, they then need to be analyzed to obtain an index of abundance. While there are many model-based options for obtaining an index [e.g. @Thorson2015], design-based approaches, such as stratified analyses, are often used. Here we apply formula presented in Smith and Somerton [-@Smith1981; equations are replicated in [*Appendix C*][Appendix C: Stratified analysis equations]] to calculate stratified estimates of total abundance ($\hat{I}_{y,k}$), abundance at length ($\hat{I}_{l,y,k}$) and abundance at age ($\hat{I}_{a,y,k}$). Note that estimates of total abundance are based on aggregate catch while abundance at length requires length frequencies to be scaled up using set-specific ratios of measured to caught fish, and these length frequencies are converted to age by applying a division-level age-length-key. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance at age estimates from each survey:

@@

Stratified estimates of abundance obtained are by supplying the output from `sim_survey` to the `run_strat` function. RMSE of the stratified estimates can then be calculated using the `strat_error` function. Results and error of a stratified analysis of one survey over a population are obtained using the following code (using default values):

@@

The relative performance of the surveys tested can be compared using `plot_survey_rank` and `plot_error_surface`. The `plot_survey_rank` function produces a divergent dot plot of the results which ranks the surveys by RMSE. Using the `which_strat` argument, the plot can be focused on total, length or age based stratified results (Figure \@ref(fig:rank)). The `plot_error_surface` focuses solely on the age based stratified results by plotting a surface of RMSE (z-axis) by set (drop down selection), length (y-axis) and age (z-axis) sampling effort. The sampling effort axes can be rule or sample size based (`plot_by = "rule"` or `plot_by = "samples"`, respectively; Figure \@ref(fig:rmse-surface)).

@@

```{r rank, fig.cap = "Divergent dot plot of the precision and accuracy (RMSE) of length based stratified estimates of abundance, and total sampling effort (number of sets [$N_{\\mathrm{sets}}$] and length measurements [$N_{\\mathrm{measured}}$]), under various sampling protocol (set density [$D_{\\mathrm{sets}}$] and maximum number of lengths measured per set [$M_{\\mathrm{lengths}}$]). Records are ranked by lowest to highest RMSE score."}

@@

```{r rmse-surface, fig.cap = "Surface plots of RMSE from an array of surveys with different sampling protocol. Panels represent surveys with different set densities ($D_{\\mathrm{sets}}$), x-axes represent the maximum sampling effort of lengths per set ($M_{\\mathrm{lengths}}$), and y-axes represent the maximum number of ages to collect per length group ($M_{\\mathrm{ages}}$). This plot is a facet of plots produced by `plot_error_surface` when supplied results from `test_surveys`. Note that the z-axes scales are different across the facets."}

@@

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell, instead fish may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. These assumptions, plus a range of others, will surely under-represent the natural variability of fish populations. Nevertheless, the **`SimSurvey`** package provides the most realistic operating model that we are aware of for simulating stratified-random survey data from a population that varies across age, year and space dimensions.

@@

The case study used here provides one example of ways in which **`SimSurvey`** can be used to simulation test the design of fisheries-independent trawl surveys. There are multiple layers to the sampling design of such surveys and the end results are linked with the way such data are analyzed. Below we outline some examples where the **`SimSurvey`** package may aid future research efforts.

@@

Assessing ages for a large number of fish is very time-consuming and, as such, length-stratified sampling is often used to estimate age frequencies of fish populations. The resultant sub-sample is used to construct an age-length key (i.e. the probability a fish is a specific age given length) and age frequencies are obtained by applying this key to length-frequencies obtained via more expansive random sampling. One age-length key is typically assumed to be representative of the whole stock area, however, spatial variability in the relationship may introduce bias in abundance-at-age estimates [@Berg2012]. Results from the case study presented here ([*Appendix A*][Appendix A: Case study]) reiterate this point and **`SimSurvey`** may serve as a platform for testing potential model-based solutions to this problem [e.g. @Berg2012].

@@

Up to now, the package has focused on the effects of sampling design on the precision and bias of population estimates obtained from fisheries-independent surveys, however, the costs associated with sampling has yet to be considered. In future iterations of **`SimSurvey`**, we hope to add options for integrating data on the time and monetary costs associated with each level of sampling (sets, length measurements, age determination) to facilitate cost-benefit analyses. We also realize that a single fisheries-independent survey may have multiple goals as data obtained are often used to assess multiple species or to conduct community analyses. We will therefore endeavor to add functions for simulating multi-species surveys. Finally, it would be useful to add an option for testing the consequences of surveys with partial coverage of a population as survey coverage is a frequent concern in stock assessment.

@@

The **`SimSurvey`** package serves as a tool for simulating stratified random surveys of dynamic populations that vary across ages, time and space. The core of the simulation is based on the widely used cohort equation and, even though the processes that define recruitment and total mortality are simple, a wide range of stock dynamics can be simulated by changing a few parameters. This base population can then be distributed through a grid and relationships with depth can be defined as can the nature of the correlation across ages, years and space. Together, two functions (`sim_abundance` and `sim_distribution`) are capable of simulating a wide range of populations with different life histories, depth associations and spatial properties. The next necessary step to generating data similar to actual observations is to conduct a survey. In this package we implement a function, `sim_survey`, that conducts a stratified random survey of the population. The sampling process is governed by the area covered by the trawl as well as age-specific catchability. Sub-sampling protocol (length and age sampling) can also be varied. As such, data from a wide range of surveys can be simulated.

@@

```{r real-sim-comp, fig.cap = "Comparison of a) real and b) simulated survey data where, from top to bottom, histograms of numbers caught across sets, distributions of set catches and length-frequency distributions from three random sets are shown from a randomly selected year from the real and simulated 3Ps cod survey data. The colors of the length-frequency plots correspond to the colored locations. The deeper shades in the length-frequency plots represent numbers of fish sampled for age determination."}

@@

Compared to increases in set density, the effects of increased length sampling effort on abundance at length estimates are less clear. Regarding estimates of abundance at length, RMSE appears to reach a plateau at when length sampling effort is increased 100 measurements per set (Figure \@ref(fig:rank)). Increasing the sampling rule above 100 measurements per set results in many more fish being measured, however, the increase in sampling effort is not matched with substantive declines in RMSE (Figure \@ref(fig:rank)). Further, it appears that measuring fewer total fish at more locations is more beneficial than measuring many fish at fewer locations (Figure \@ref(fig:rank)).

@@

While much work has yet to be done, results from the simple simulation echo the growing body of literature which concludes that extra sub-sampling is an ineffective means of improving estimates relative to sampling more locations [@Pennington1994; @Pennington2002; @Stewart2014; @Bogstad1995; @Coggins2013; @Zhang2013]. In general, the most significant source of variation in fisheries-independent surveys stems from set-to-set variation, and not variability from individual sub-samples. This is largely because fish caught together tend to be more similar than those in the general population [@Pennington1994]. Therefore, if the goal of a trawl survey is to maximize information, it is likely better to stop collecting correlated samples and, instead, focus efforts on other species or the next set. This is simply one example of the questions that can be explored using **`SimSurvey`**.

>>>>

**1\.** Age-structured fish stocks often show complex spatial and temporal dynamics, creating challenges in designing and implementing effective population surveys. Inappropriate sampling designs can potentially lead to both under-sampling (reducing precision and increasing the risk of bias) and over-sampling (through the extensive and potentially expensive sampling of correlated metrics).

**2\.** For assessments based on fisheries-independent surveys, the ability to estimate population parameters is affected by multiple levels of sampling, such as the number of fishing sets as well as the sub-sampling of fish captured to measure biological characteristics (e.g. lengths or ages). Population estimates are also affected by the pathway taken to analyze such data.

**3\.** Though simulations are a useful tool for exploring the efficacy of specific sampling strategies and statistical methods, there are a limited the number of tools that facilitate the simulation testing of a range of sampling and analytical pathways for fisheries-independent survey data.

**4\.** Here we introduce the `R` package **`SimSurvey`**, which has been designed to simplify the process of simulating surveys of age-structured and spatially-distributed fish populations. The package allows the user to simulate age-structured populations that vary in space and time and explore the efficacy of a range of sampling protocols to reproduce the population parameters of the known population. **`SimSurvey`** also include a function for running a stratified-random analysis of the simulated data.

**5\.** **`SimSurvey`** can serve as a convenient, accessible and flexible platform for simulating a wide range of sampling strategies for fish stocks that show complex structuring. Various statistical approaches can then be applied to the results to test the efficacy of different analytical approaches.

@@

Fisheries-independent surveys have become a mainstay in the management of dynamic fish stocks as they provide indices of population abundance as well as estimates of various population characteristics such as length and age frequencies. While costly to obtain, this information forms the basis of many stock assessments throughout the world [@Pennington1998]. Efficient and informed management decisions therefore require surveys and analyses that maximize information while minimizing the expense of data collection. While simulations provide a platform for exploring solutions to this optimization problem, building the necessary simulation framework is not a trivial task given the multi-stage nature of the typical sampling program and the complexity of the population processes we aim to represent. Notably, many fish stocks show size-specific patterns of aggregation, making it difficult to collect biological sub-samples (e.g. lengths and ages) that are representative of the entire target population. This undermines the assumptions of many analyses as sub-samples from such populations tend to exhibit strong positive intracluster correlation [@Aanes2015]. These complexities may explain why simulations that test the full sampling and analytical pathway of fisheries-independent surveys are rare [but see @puerta2019; @schnute2003].

Here we document **`SimSurvey`**, an `R` package designed to simplify and facilitate realistic simulations of fisheries-independent trawl surveys. In short, the package allows for the simulation of random or stratified-random surveys of an age-structured population that varies in space and time. The package has two main components: the first focuses on mimicking realistic fish stocks by simulating a spatially and age-correlated population distributed across a habitat gradient, and the second component focuses on simulating various surveys of these virtual fish stocks.

This simulation framework has similarities to those presented by Schnute and Haigh [-@schnute2003] and Puerta et al. [-@puerta2019], however, efforts were focused on developing a series of general and accessible functions to simplify the process of testing multiple sampling scenarios and analytical pathways. The steps taken to simulate surveys of spatial, age-structure populations are outlined below. While the core of this paper focuses on how to use this package, it is important to note that the defaults of the package are based on a case study. Output from default function calls are therefore relavant to the case study and these results are described and discussed in [*Appendix A*][Appendix A: Case study].

@@

Table: (\#tab:fun) Names and descritpions of the key functions of **`SimSurvey`**. Functions in bold font are core functions and those in medium font are designed for use inside the core functions. The latter are typically closures, which are functions that contain data and return functions [@wickham2014]; here they are used to store parameter values and return functions that require dimensions, such as ages or years, to be supplied.

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or dispersion of abundance around the mean depth. This helps simulate depth preferences of particular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation within ages and years, and the two dimension AR1 age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations are controlled by a smoothing ($\lambda$) and a scaling parameter ($\kappa$) [here $\kappa$ is approximated from the range parameter ($r$), $\kappa = \sqrt{8 \lambda} / r$; @Blangiardo2015] and correlation across ages and years is controlled by $\varphi_{\xi, \mathrm{age}}$ and $\varphi_{\xi, \mathrm{year}}$, respectively. The overall variance of the process is controlled by $\sigma_{\xi}^2$ (see [*Appendix B*][Appendix B: Age-year-space covariance] for a more detailed description of the space-age-year covariance structure). In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid.

@@

This function retains all the data simulated by `sim_abundance` and adds a data.table [@dowle2017], named `sp_N`, with abundance (`N`) split by `age`, `year` and `cell`. The function also retains the grid object and converts these data into a data.table, named `grid_xy`, with headers `x`, `y`, `depth`, `cell`, `division` and `strat`. The `sp_N` object can be merged with the `grid_xy` data by `cell` to associate abundance with specific locations, depth, divisions or strata. The `plot_distribution` function can be used to provide a quick visual of the distribution across ages and years. The code below will generate interactive plots with an Age-Year slider, however, for this paper we present a facet plot of the simulated data (Figure \@ref(fig:distribution)).

@@

The final step in the simulation is to conduct a stratified random survey over the age-year-space array generated. The area of each strata is calculated and this is used to define the number of sets allocated to each strata under a particular set density, $D_{\mathrm{sets}}$. The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

@@

The function `sim_survey` can be used to simulate data from one survey over a population created using `sim_distribution`. A default function call is described in Table \@ref(tab:survey). The `sim_survey` function simulates the sampling process of the survey and, as such, requires a closure for defining catchability as a function of age and definitions of the design of the survey. Specifically, the `q` argument requires a closure, such as `sim_logistic`, for defining the probability of catching specific age groups, trawl dimensions are defined in the `trawl_dim` argument, and set, length and age sampling effort are defined using the `set_den`, `lengths_cap` and `ages_cap` arguments, respectively. Like `sim_abundance` and `sim_distribution`, custom closures can be supplied to `sim_survey` to impose alternate parametric curves for catchability at age. Multiple simulations of the same survey can be run using the `n_sims` argument, however, requesting large numbers of simulations can be computationally demanding depending on the processing capacity available. Below we use `sim_survey` to simulate two surveys over a default population, of which one is set-up to have higher set density (`set_den`) than the other.

@@

```{r survey, fig.cap = "Bubble plots of abundance and histograms of set catches from a simulated stratified-random survey of a default population under relatively a) low and b) high sampling effort. Point size and color are scaled by abundance in the bubble plots. Histograms of length and age composition include the distribution of all fish caught next to those sampled overlaid with a line of the true distribution of lengths and ages available to the survey. Note that the first simulation of the survey in year 20 is depicted here. These plots are produced by `plot_survey` when supplied survey data simulated using `sim_survey`."}

@@

As noted above, available RAM may limit the utility of the `sim_survey` function for running thousands of simulations of the same survey. The `sim_survey_parallel` function was therefore constructed to facilitate this process. This function is set-up to run multiple `sim_survey` calls in parallel using the **`doParallel`** package [@weston2015] and, as such, multiple loops can be run using the `n_loops` argument and, within each loop, multiple simulations can be run (controlled using the `n_sims` argument). Total simulations will be the product of `n_loops` and `n_sims` arguments. If more than one core (`cores`) is specified, then the simulations will be run in parallel to speed up the process. Low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower. The optimum ratio of `n_sims` to `n_loops` will depend on the amount of RAM and number of cores in a given computer. In any case, this function simplifies the process of running thousands of simulations of the same survey and the simulated data can then be supplied to survey-based or model-based analyses that require simulation testing.

@@

Survey data need to be analyzed to obtain an index of abundance. While there are many model-based options for obtaining an index [e.g. @Thorson2015], design-based approaches, such as stratified analyses, are often used. Here we apply formula presented in Smith and Somerton [-@Smith1981; equations are replicated in [*Appendix C*][Appendix C: Stratified analysis equations]] to calculate stratified estimates of total abundance ($\hat{I}_{y,k}$), abundance at length ($\hat{I}_{l,y,k}$) and abundance at age ($\hat{I}_{a,y,k}$). Note that estimates of total abundance are based on aggregate catch while abundance at length requires length frequencies to be scaled up using set-specific ratios of measured to caught fish, and these length frequencies are converted to age by applying a division-level age-length-key. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance at age estimates from each survey:

@@

Stratified estimates of abundance are obtained by supplying the output from `sim_survey` to the `run_strat` function. RMSE of the stratified estimates can then be calculated using the `strat_error` function. Results and error of a stratified analysis of one survey over a population are obtained using the following code (using default values):

@@

The relative performance of the surveys tested can be compared using `plot_survey_rank` and `plot_error_surface`. The `plot_survey_rank` function produces a divergent dot plot of the results which ranks the surveys by RMSE. Using the `which_strat` argument, the plot can be focused on total, length or age based stratified results (Figure \@ref(fig:rank)). The `plot_error_surface` displays the age based stratified results by plotting a surface of RMSE (z-axis) by set (drop down selection), length (y-axis) and age (z-axis) sampling effort. The sampling effort axes can be rule or sample size based (`plot_by = "rule"` or `plot_by = "samples"`, respectively; Figure \@ref(fig:rmse-surface)).

@@

```{r rank, fig.cap = "Divergent dot plot of the precision and accuracy (RMSE) of length based stratified estimates of abundance, and total sampling effort (number of sets [$N_{\\mathrm{sets}}$] and length measurements [$N_{\\mathrm{measured}}$]), under various sampling protocols (set density [$D_{\\mathrm{sets}}$] and maximum number of lengths measured per set [$M_{\\mathrm{lengths}}$]). Records are ranked by lowest to highest RMSE score. Within each plot, a color ramp is applied from lowest to highest value as an additional visual aid. Note that the exponent format of the axes defaults to SI unit symbols (e.g. M for million)."}

@@

```{r rmse-surface, fig.cap = "Surface plots of RMSE from an array of surveys with different sampling protocol. Panels represent surveys with different set densities ($D_{\\mathrm{sets}}$), x-axes represent the maximum sampling effort of lengths per set ($M_{\\mathrm{lengths}}$), and y-axes represent the maximum number of ages to collect per length group ($M_{\\mathrm{ages}}$). This plot is a facet of plots produced by `plot_error_surface` when supplied results from `test_surveys`. Note that RMSE scales are different across $D_{\\mathrm{sets}}$ facets. Note that the exponent format of the axes defaults to SI unit symbols (e.g. M for million)."}

@@

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell, instead fish may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. These assumptions, plus a range of others, will surely under-represent the natural variability of fish populations and survey protocol. Nevertheless, the **`SimSurvey`** package provides the most realistic operating model that we are aware of for simulating stratified-random survey data from a population that varies across age, year and space dimensions.

<!-- # Should we include a summary of the case study - previous abstrat included below -->

<!-- A central question to fish stock assessments is: how many samples are needed to adequately represent the population being monitored? For assessments based on trawl surveys, our ability to estimate population characteristics, such as abundance at age, is affected by multiple levels of sampling (i.e. the number of sets, lengths and ages sampled in a survey). We therefore need to assess the impact of haul design and length and age sampling on survey accuracy to determine optimal sampling effort. In this study we simulated repeated stratified-random samples from a spatially correlated field of simulated fish. These samples were then analyzed and estimates of abundance at age were compared against a known truth. By varying the sampling protocol, we demonstrate that increasing the number of sets conducted per stratum provides the greatest gains in precision when sampling a clustered population. Increasing length and age sampling efforts also improved abundance estimates, but to a lesser extent and improvements were typically marginal, and sometimes squandered, when sub-sampling effort was increased. These results indicate that high levels of length and age sampling effort can be scaled back without significant losses to precision and, in some cases, estimates of abundance at age may be improved by reducing sub-sampling effort. Time saved by reducing said sampling may afford more time to conduct additional sets and/or increase sampling efforts of other species. While this simulation is tailored to a specific case, the method may be adapted to different systems and survey procedures. -->

@@

The case study described in [*Appendix A*][Appendix A: Case study] provides one example of ways in which **`SimSurvey`** can be used to simulation test the design of fisheries-independent trawl surveys. There are multiple layers to the sampling design of such surveys and the end results are linked with the way such data are analyzed. Below we outline some examples where the **`SimSurvey`** package may aid future research efforts.

@@

Assessing ages for a large number of fish is very time-consuming and, as such, length-stratified sampling is often used to estimate age frequencies of fish populations. The resultant sub-sample is used to construct an age-length key (i.e. the probability a fish is a specific age given length) and age frequencies are obtained by applying this key to length-frequencies obtained via more expansive random sampling. One age-length key is typically assumed to be representative of the whole stock area, however, spatial variability in the relationship may introduce bias in abundance-at-age estimates [@Berg2012]. Results from the case study (see [*Appendix A*][Appendix A: Case study]) reiterate this point and **`SimSurvey`** may serve as a platform for testing potential model-based solutions to this problem [e.g. @Berg2012].

@@

Up to now, the package has focused on the effects of sampling design on the precision and bias of population estimates obtained from fisheries-independent surveys; however, the costs associated with sampling has yet to be considered. In future iterations of **`SimSurvey`**, we hope to add options for integrating data on the time and monetary costs associated with each level of sampling (sets, length measurements, age determination) to facilitate cost-benefit analyses. We also realize that a single fisheries-independent survey may have multiple goals as data obtained are often used to assess multiple species or to conduct community analyses. We will therefore endeavor to add functions for simulating multi-species surveys. Finally, it would be useful to add an option for testing the consequences of surveys with partial coverage of a population as survey coverage is a frequent concern in stock assessment.

@@

The **`SimSurvey`** package serves as a tool for simulating stratified random surveys of dynamic populations that vary across ages, time and space. The core of the simulation is based on the widely used cohort equation and, even though the processes that define recruitment and total mortality are simple, a wide range of stock dynamics can be simulated by changing a few parameters. This base population can then be distributed through a grid and relationships with depth can be defined as can the nature of the correlation across ages, years and space. Together, two functions (`sim_abundance` and `sim_distribution`) are capable of simulating a wide range of populations with different life histories, depth associations and spatial properties. The next necessary steps to generating data similar to actual observations is to conduct a survey. In this package we implement a function, `sim_survey`, that conducts a stratified random survey of the population. The sampling process is governed by the area covered by the trawl as well as age-specific catchability. Sub-sampling protocol (length and age sampling) can also be varied. As such, data from a wide range of surveys can be simulated.

@@

```{r real-sim-comp, fig.cap = "Comparison of a) real and b) simulated survey data where, from top to bottom, histograms of numbers caught across sets, distributions of set catches, and length-frequency distributions from three random sets are shown from a randomly selected year from the real and simulated 3Ps cod survey data. The colors of the length-frequency plots correspond to the colored locations. The deeper shades in the length-frequency plots represent numbers of fish sampled for age determination."}

@@

Compared to increases in set density, the effects of increased length sampling effort on abundance at length estimates are less clear. Regarding estimates of abundance at length, RMSE appears to reach a plateau at when length sampling effort is increased to 100 measurements per set (Figure \@ref(fig:rank)). Increasing the sampling rule above 100 measurements per set results in many more fish being measured, however, the increase in sampling effort is not matched with substantive declines in RMSE (Figure \@ref(fig:rank)). Further, it appears that measuring fewer total fish at more locations is more beneficial than measuring many fish at fewer locations (Figure \@ref(fig:rank)).

@@

While much work has yet to be done, results from the simple simulation echo the growing body of literature which concludes that extra sub-sampling is an ineffective means of improving estimates relative to sampling more locations [@Pennington1994; @Pennington2002; @Stewart2014; @Bogstad1995; @Coggins2013; @Zhang2013]. In general, the most significant source of variation in fisheries-independent surveys stems from set-to-set variation, and not variability from individual sub-samples. This is largely because fish caught together tend to be more similar than those in the general population [@Pennington1994]. Therefore, if the goal of a trawl survey is to maximize information, it is likely better to stop collecting correlated samples and, instead, focus efforts the next set and/or other species. This is simply one example of the questions that can be explored using **`SimSurvey`**.
